DMRGenie: Graphical interface for entanglement renormalization

### 2025-12-03 paper/paper.tex
Add files via upload

We discuss implementation of a graphical user interface for tensor operations in scientific simulations related to entanglement renormalization. We call this software DMRGenie based on its heavy reliance on Genie which is a well-known software package for web applications. We also discuss the deployment of the software. Scientific simulations with tensor network-based framework of quantum algorithm methods are now possible through this tool without lengthy start-up or learning times.

>>>>

We discuss implementation of a graphical user interface for tensor operations in scientific simulations related to entanglement renormalization. We call this software DMRGenie based on its heavy reliance on Genie which is a well-known software package for web applications. We also discuss the deployment of the software. Scientific simulations with a tensor network-based framework of quantum algorithm methods are now possible through this tool without lengthy start-up or learning times.
